The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2017-03-17 manuscript/acronyms.tex
add apob and afp acronyms; remove psg and pag acronyms

\DeclareAcronym{PSG}{short=PSG,long={Pregnancy-Specific Glycoprotein}}
\DeclareAcronym{PAG}{short=PAG,long={Pregnancy-Associated Glycoprotein}}

@@

>>>>

%\DeclareAcronym{PSG}{short=PSG,long=Pregnancy-Specific Glycoprotein}
%\DeclareAcronym{PAG}{short=PAG,long=Pregnancy-Associated Glycoprotein}

@@

\DeclareAcronym{AFP}{short=\href{http://www.genenames.org/cgi-bin/gene_symbol_report?match=AFP}{\textit{AFP}},long={alpha fetoprotein},first-style=reversed,single={\href{http://www.genenames.org/cgi-bin/gene_symbol_report?match=AFP}{\textit{AFP}} (alpha fetoprotein)}}
\DeclareAcronym{APOB}{short=\href{http://www.genenames.org/cgi-bin/gene_symbol_report?match=APOB}{\textit{APOB}},long={apolipoprotein B},first-style=reversed,single={\href{http://www.genenames.org/cgi-bin/gene_symbol_report?match=APOB}{\textit{APOB}} (apolipoprotein B)}}
